01 - Simulate data

### 2023-12-09 scripts/01_sim_data.qmd
fixes https://github.com/stefanocoretta/gamm_biling/issues/1#issuecomment-1847441336

dat2 %>%
  filter(subj == 1, group == "es_0") %>%
  ggplot(aes(timep, eud, group = id, colour = as.factor(rep))) +
  geom_path() +
  facet_grid(cols = vars(vowel))
```

>>>>

dat2 %>%
  filter(subj == "es_0_1") %>%
  ggplot(aes(timep, eud, group = id, colour = as.factor(rep))) +
  geom_path() +
  facet_grid(cols = vars(vowel))
```
